---
title: "Star Wars Opinion Data"
author: "Angela Zoss"
date: "2/18/19"
output: html_document
---

## Setup your environment

```{r}

# Load required libraries

library(tidyverse)

```

## Load your data

```{r}

# data from https://fivethirtyeight.com/features/americas-favorite-star-wars-movies-and-least-favorite-characters/
# note: CSV has two rows of headers, so I have manually created a list of headers and am adding
# that after loading just the data rows
# also extracting just the opinion columns and reshaping them to long data format

new_names <- read_csv('data/StarWarsNames.csv') %>% select(NewNames)
  
starwars_opins <- read_csv('data/StarWars.csv', skip=2, col_names=FALSE) %>% setNames(unlist(new_names)) %>% dplyr::select(RespondentID, starts_with("Opinion")) %>% gather("Character","Opinion",-RespondentID) %>% mutate(Character=sub("Opinion","",Character)) %>% na.omit()

```

## Plot the opinions for Han Solo

```{r}

# hint: there is a geom that will take a categorical variable and count the data points in
# each category


```

## Plot the opinions for Jar Jar Binks

```{r}


```

## Edit the axes of each of these charts to make them comparable

```{r}

# remember, editing an axis usually requires a scale


```

## Advanced: can you think of another way to standardize the axes?

```{r}


```

## Reorder the opinion levels so they are in a logical order

```{r}

opinion.levels <- c("Unfamiliar (N/A)","Very unfavorably","Somewhat unfavorably",
                    "Neither favorably nor unfavorably (neutral)",
                    "Somewhat favorably","Very favorably")

starwars_opins <- starwars_opins %>% 
         mutate(Opinion=factor(Opinion, opinion.levels))


```

## Flip the axes so the opinion levels are on the y-axis

```{r}


```

## Use a different color for each opinion level

```{r}


```

## Customize the color palette

```{r}

# hint: editing colors requires a change of scale
# can google "R colors" for a list of all named colors

opinion.colors <- c("grey50","firebrick4","firebrick1","grey85","dodgerblue1","dodgerblue4")



```

## Show Han Solo answers as stacked bars instead

```{r}



```

## Use custom color scale

```{r}


```

## Add Jar Jar Binks as a new bar

```{r}


```

## Turn the bars sideways

```{r}


```

## Use fct_rev() to reverse the factor levels for the fill variable

```{r}


```

## Reverse opinion.colors with rev() to reverse the color vector

```{r}



```

## Add all characters into plot

```{r}



```

## Sort characters (ascending) by their average opinion

```{r}

# hint: use "fct_reorder" to order Character by Opinion
# you will have to find a way to treat Opinion as a number




```



